\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

\geometry{left=2.5cm, right=2.5cm, top=1.5cm, bottom=1.5cm}
\pagenumbering{gobble}
\definecolor{primaryColor}{RGB}{0, 102, 204}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5ex}

\newcommand{\entrytitle}[3]{
    \noindent\textbf{#1}, #2\hfill#3
}

\newlist{details}{itemize}{1}
\setlist[details]{
    label=\textbullet,
    leftmargin=1.5em,
    topsep=0.2ex,
    partopsep=-0pt,
    itemsep=0.2ex,
    parsep=0pt
}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    filecolor=primaryColor,
    urlcolor=primaryColor,
    citecolor=primaryColor,
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\newcommand{\sectiontitle}[1]{\vspace{3mm}{\color{primaryColor}\noindent\textbf{#1}}\vspace{1.5mm}\hrule\vspace{2mm}}
\newcommand{\experience}[4]{\textbf{#1}, #2 \hfill \vspace{-4mm}#3\\#4\vspace{3mm}}

\begin{document}

\begin{center}
    \LARGE{\textbf{\color{primaryColor}Roman Knyazhitskiy}}\\
    \vspace{2mm}
    \normalsize{
        \faEnvelope~\href{mailto:cv@knyaz.tech}{cv@knyaz.tech} \quad|\quad
        \faGlobe~\href{https://knyaz.tech}{knyaz.tech} \quad|\quad
        \faGithub~\href{https://github.com/knyazer}{knyazer}
    }
\end{center}

\sectiontitle{Summary}
\noindent
Master's student with a strong focus on Generative AI, specializing in transformer-based models and implicit neural representations. Extensive hands-on experience in JAX and PyTorch, demonstrated by building a GPT language model and an INR-based image compressor from scratch. Experienced in designing and running large-scale ML experiments, researching diffusion models, and prototyping end-to-end applications.

\vspace{-2mm}


\sectiontitle{Education}

\entrytitle{MPhil in MLMI (Machine Learning)}{University of Cambridge}{10/2025 - 09/2026}

\entrytitle{BSc Computer Science and Engineering}{TU Delft}{09/2022 - 07/2025}
\begin{details}
    \item GPA: 8.7/10. Distinction (cum laude, top 5\%) + Honours.
\end{details}

\vspace{-2mm}


\sectiontitle{Publications}

\vspace{-5mm}

\renewcommand{\refname}{}
\renewcommand{\refname}{\vspace{-\baselineskip}}

\bibliographystyle{unsrt}
\nocite{*}
\bibliography{pub}

\vspace{-3mm}

\sectiontitle{Work Experience}

\entrytitle{Machine Learning Engineer}{Delft Mercurians}{05/2023 - 09/2025}
\begin{details}
    \item Started out as an indidual contributor, grew the team to 5 people over two years.
    \item Built a JAX-based continuous-time differentiable simulator for training control models.
    \item Designed and implemented a Model Predictive Control (MPC) system for real-time optimization.
\end{details}

\entrytitle{Research Associate}{TU Delft}{03/2023 - 08/2025}
\begin{details}
    \item Researched applications of generative models, including LLMs for code generation and transformer-based Prior-Data Fitted Networks (PFNs) for meta-learning.
    \item Participated in academic discussions on diffusion models and advanced optimization methods.
\end{details}

\entrytitle{Applied Machine Learning Intern}{Central Robotics Institute}{06/2021 - 07/2021}
\begin{details}
    \item Developed computer vision algorithms for a robotic drawing application, converting images to line art.
\end{details}

\vspace{-2mm}

\sectiontitle{Selected Projects}

\entrytitle{Nano JAX GPT}{JAX, Equinox, Deep Learning}{2023}
\begin{details}
    \item Implemented a high-performance GPT language model from scratch in JAX and Equinox, architected for distributed training with mixed precision and memory-efficient gradient accumulation.
    \item Explored speculative decoding, multi-token prediction, and structured embedding sparsity for optimized inference.
\end{details}

\entrytitle{Nano JAX Implicit Neural Representations}{Python, JAX, Equinox, Computer Vision}{2024}
\begin{details}
    \item Developed an INR framework for image compression, learning continuous neural functions that map 2D coordinates to pixel values.
    \item Implemented adaptive latent point sampling based on image gradients and a multi-stage training pipeline with JIT compilation and multi-GPU sharding for efficiency.
\end{details}

\entrytitle{IEFT-PFN for Hyperparameter Optimization}{JAX, Equinox, Transformers, AutoML}{2025}
\begin{details}
    \item Built a Prior-Data Fitted Network (PFN) using a causal transformer to predict ML training curves, accelerating hyperparameter optimization through in-context learning.
    \item Designed a probabilistic histogram decoder for uncertainty-aware predictions and a multi-stage curriculum for training on synthetic and real benchmark data.
\end{details}

\entrytitle{Weather Forecasting with Normalizing Flows}{Python, JAX/Equinox, Generative Models}{2025}
\begin{details}
    \item Developed an end-to-end system for probabilistic weather forecasting using Continuous Normalizing Flow (CNF) models in JAX, a type of generative model, for uncertainty-calibrated predictions.
\end{details}

\entrytitle{Silver-qt: Sign Language Recognition System}{Python, PyQt, ONNX, Computer Vision}{2019}
\begin{details}
    \item Developed an end-to-end prototype for real-time sign language recognition using a multi-stage vision pipeline (YOLOv5, Autoencoder, LSTM) and built a cross-platform GUI with PyQt.
\end{details}

\vspace{-2mm}

\sectiontitle{Open Source Contributions}
\begin{itemize}
    \item Enhanced functionalities in the JAX ecosystem, contributing to \href{https://github.com/google/jaxtyping}{jaxtyping}, \href{https://github.com/patrick-kidger/equinox}{Equinox}, and \href{https://github.com/RobertTLange/gymnax}{Gymnax}.
    \item Improved libccd (C++ collision detection library) by fixing a critical infinite loop bug.
\end{itemize}

\vspace{-2mm}

\sectiontitle{Honours and Awards}
\begin{itemize}
    \item \textbf{1st Place}, Bunq Hackathon 6 (2025).
    \item \textbf{2nd Place \& Special Prize}, Epoch AI Hackathon (2024).
    \item \textbf{Best Software Solution}, RoboCup World Championships, Sydney (2019).
    \item \textbf{Silver Medal}, AIIJC International AI Competition for Juniors for Sign Language recognition app.
\end{itemize}

\end{document}
