\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

\geometry{left=1.5cm, right=1.5cm, top=1.5cm, bottom=1cm}
\pagenumbering{gobble}
\definecolor{primaryColor}{RGB}{0, 102, 204}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.0ex}

\newcommand{\entrytitle}[3]{
    \noindent\textbf{#1}, #2\hfill#3
}

\newlist{details}{itemize}{1}
\setlist[details]{
    label=\textbullet,
    leftmargin=1.5em,
    topsep=0.1ex,
    partopsep=-0pt,
    itemsep=0.1ex,
    parsep=0pt
}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    filecolor=primaryColor,
    urlcolor=primaryColor,
    citecolor=primaryColor,
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\newcommand{\sectiontitle}[1]{\vspace{0mm}{\color{primaryColor}\noindent\textbf{#1}}\vspace{1.0mm}\hrule\vspace{1mm}}
\newcommand{\experience}[4]{\textbf{#1}, #2 \hfill \vspace{-4mm}#3\\#4}

\begin{document}

\begin{center}
    \LARGE{\textbf{\color{primaryColor}Roman Knyazhitskiy}}\\
    \vspace{2mm}
    \normalsize{
        \faEnvelope~\href{mailto:cv@knyaz.tech}{cv@knyaz.tech} \quad|\quad
        \faGlobe~\href{https://knyaz.tech}{knyaz.tech} \quad|\quad
        \faGithub~\href{https://github.com/knyazer}{knyazer}
    }
\end{center}
\vspace{-3mm}

\sectiontitle{Summary}
\noindent
MPhil in Machine Learning student at the University of Cambridge with some research in robotics, reinforcement and deep learning. Experienced in developing and scaling novel algorithms for medium-scale problems, with lots of hands-on experience in JAX, Python, and C++. Proven ability to lead research projects in AutoML, LLMs, and optimization, including contributions to Google's open-source JAX ecosystem.

\sectiontitle{Education}

\entrytitle{MPhil in MLMI (Machine Learning)}{University of Cambridge}{10/2025 - 08/2026}

\entrytitle{BSc Computer Science and Engineering}{TU Delft}{09/2022 - 07/2025}
\begin{details}
    \item GPA: 8.7/10. Cum Laude + Honours.
\end{details}

\sectiontitle{Work Experience}

\entrytitle{Research Associate}{TU Delft}{03/2023 - 08/2025}
\begin{details}
    \item Collaborated on research projects in AutoML, Meta Learning, and LLM applications for code generation.
    \item Investigated and presented on advanced optimization methods (e.g., Shampoo) and generative models.
\end{details}

\entrytitle{Machine Learning Engineer}{Delft Mercurians (RoboCup Team)}{05/2023 - 09/2025}
\begin{details}
    \item Led development of AI control systems, including a real-time Model Predictive Control (MPC) system.
    \item Built a bespoke continuous-time differentiable physics simulator from scratch in JAX and Equinox.
    \item Integrated Python ML models into a high-performance Rust codebase for controlling autonomous robots.
\end{details}

\sectiontitle{Publications}
\vspace{-5mm}
\renewcommand{\refname}{}
\renewcommand{\refname}{\vspace{-\baselineskip}}
\bibliographystyle{unsrt}
\nocite{*}
\bibliography{pub}

\vspace{-5mm}
\sectiontitle{Selected Research Projects}

\entrytitle{IEFT-PFN: Transformers for Hyperparameter Optimization}{JAX, AutoML, Meta Learning}{2025}
\begin{details}
    \item Developed a transformer-based Prior-Data Fitted Network (PFN) for HPO using in-context learning to predict training curves, achieving a 15-20\% MMedLL improvement over the IFBO baseline.
    \item Implemented a multi-stage training curriculum using both synthetic and real curve data.
\end{details}

\entrytitle{Lyapunov-Stabilized RL for Continuous Control}{JAX, Deep RL, Physics Simulation}{2024}
\begin{details}
    \item Implemented a novel reinforcement learning framework using Lyapunov stability factors to stabilize truncated backpropagation through time in long-horizon, continuous control tasks.
\end{details}


\sectiontitle{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python, C++, C, Rust, Go, MATLAB
    \item \textbf{ML/DL Frameworks:} JAX/Equinox, PyTorch, ONNX
    \item \textbf{Systems:} Distributed Computing, Linux, Docker, CI/CD
\end{itemize}

\sectiontitle{Open Source Contributions}
\begin{itemize}
    \item \textbf{Google (jaxtyping):} Contributed enhancements to core functionality.
    \item \textbf{Equinox:} Resolved issues and contributed to the widely used JAX neural network library.
    \item \textbf{libccd:} Fixed a critical infinite loop bug in the C++ robotics collision detection library.
\end{itemize}

\sectiontitle{Honours and Awards}
\begin{itemize}
    \item \textbf{1st Place}, Bunq Hackathon 6 (2025) -- €30,000 prize
    \item \textbf{2nd Place \& Special Prize}, Epoch AI Hackathon (2024)
    \item \textbf{Best Software Solution}, RoboCup World Championships, Sydney (2019)
    \item \textbf{Silver Medal}, AIIJC International AI Competition for Juniors
\end{itemize}

\end{document}
