\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

\geometry{left=1.5cm, right=1.5cm, top=1.5cm, bottom=1cm}
\pagenumbering{gobble}
\definecolor{primaryColor}{RGB}{0, 102, 204}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5ex}

\newcommand{\entrytitle}[3]{
    \vspace{-1mm}\noindent\textbf{#1}, #2\hfill#3\vspace{-2mm}
}

\newlist{details}{itemize}{1}
\setlist[details]{
    label=\textbullet,
    leftmargin=1.5em,
    topsep=0.1ex,
    partopsep=-0pt,
    itemsep=-0.2ex,
    parsep=0pt
}

\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    filecolor=primaryColor,
    urlcolor=primaryColor,
    citecolor=primaryColor,
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\newcommand{\sectiontitle}[1]{\vspace{1mm}{\color{primaryColor}\noindent\textbf{#1}}\vspace{1.5mm}\hrule\vspace{1mm}}
\newcommand{\experience}[4]{\textbf{#1}, #2 \hfill \vspace{-4mm}#3\\#4}

\begin{document}

\begin{center}
    \LARGE{\textbf{\color{primaryColor}Roman Knyazhitskiy}}\\
    \vspace{2mm}
    \normalsize{
        \faEnvelope~\href{mailto:cv@knyaz.tech}{cv@knyaz.tech} \quad|\quad
        \faGlobe~\href{https://knyaz.tech}{knyaz.tech} \quad|\quad
        \faGithub~\href{https://github.com/knyazer}{knyazer}
    }
\end{center}

\vspace{-5mm}

\sectiontitle{Summary}
Software Engineer and Machine Learning Researcher specializing in C++ and Python, with extensive experience in Generative AI (LLMs) and Reinforcement Learning. Proven track record of building scalable end-to-end ML systems, optimizing infrastructure, and developing accessible technologies. Expertise in JAX, algorithms, and sequential decision-making logic.

\sectiontitle{Education}

\entrytitle{MPhil in MLMI (Machine Learning)}{University of Cambridge}{10/2025 - 09/2026}

\vspace{2mm}

\entrytitle{BSc Computer Science and Engineering}{TU Delft}{09/2022 - 07/2025}
\begin{details}
    \item GPA: 8.7/10. Distinction (Cum Laude, top 5\%) + Honours.
\end{details}

\sectiontitle{Work Experience}

\entrytitle{Machine Learning Engineer (Lead)}{Delft Mercurians}{05/2023 - 09/2025}
\begin{details}
    \item Led the control team, focusing on sequential decision making and real-time optimization.
    \item Built a JAX+Equinox differentiable simulator, integrating Python models into a Rust/C++ codebase.
    \item Designed Model Predictive Control (MPC) systems for trajectory optimization.
\end{details}

\entrytitle{Research Associate}{TU Delft}{03/2023 - 08/2025}
\begin{details}
    \item Investigated Prior-Data Fitted Networks (PFNs) for meta-learning and HPO.
    \item Researched applicability of LLMs for vulnerability detection and code generation.
\end{details}

\entrytitle{Applied Machine Learning Intern}{Central Robotics Institute}{06/2021 - 07/2021}
\begin{details}
    \item Implemented image segmentation and processing logic for path planning over image edges.
\end{details}

\sectiontitle{Selected Projects}

\entrytitle{Bootstrapped DQN Scaling Laws (Reinforcement Learning)}{JAX, Deep RL}{2025}
\begin{details}
    \item Conducted large-scale empirical study of ensemble-based exploration in Deep RL.
    \item Engineered high-performance training infrastructure supporting 40,000+ configurations.
\end{details}

\entrytitle{Automatic Item Selling \& Haggling}{PyTorch, LLMs}{2025}
\begin{details}
    \item Built a system for automatic placement of the adverts on a marketplace from a photo of the item.
    \item Used a chain of LLM/VLM calls, some processing and automatic interaction with a web UI.
    \item Implement an integration that allows the system to haggle with buyers until the best price is reached.
    \item The same system was later built by the marketplace itself, probably driving some revenue.
\end{details}

\entrytitle{Implicit Neural Representations}{Python, JAX, Computer Vision}{2024}
\begin{details}
    \item Developed a framework for training memory-efficient INRs for image compression.
    \item Implemented end-to-end training pipelines with multi-GPU sharding and automatic batch scaling.
    \item Published as a workshop paper on ICLR.
\end{details}

\entrytitle{Silver-qt: Sign Language Recognition (Accessible Tech)}{Python, ONNX, CV}{2019}
\begin{details}
    \item Developed a real-time sign language platform recognition using YOLOv5 and LSTMs.
    \item Deployed several models using ONNX Runtime, integrating with a PyQt5 GUI.
\end{details}

\entrytitle{Literature Search Engine Startup (CTO)}{Python, LLM, BERT, Search}{2024}
\begin{details}
    \item Architected a recommendation and search system using fine-tuned BERT models and LLM-based scoring.
    \item Implemented embedding-based retrieval and keyword filtering to rank scientific papers.
\end{details}

\sectiontitle{Honours, Awards, Contributions}
\begin{itemize}
    \item \textbf{1st Place}, Bunq Hackathon 6 (2025) -- €30,000 prize.
    \item \textbf{2nd Place}, Epoch AI Hackathon (2024).
    \item \textbf{Best Software Solution}, RoboCup World Championships (2019).
    \item \textbf{Silver Medal}, AIIJC International AI Competition -- Sign language recognition application.
    \item \textbf{Open Source:} Contributed to \href{https://github.com/google/jaxtyping}{jaxtyping}, \href{https://github.com/patrick-kidger/equinox}{Equinox}, and \href{https://github.com/RobertTLange/gymnax}{Gymnax} (RL environments). Improved stability in libccd (C++ collision detection).
\end{itemize}

\end{document}
